PANCHANGE_analysis

### 2020-11-13 PANCHANGE_analysis.Rmd

---
title: "PANCHANGE_analysis"
author: "Katherine N Thompson, Christopher Hüebel, Molly R Davies, Kirstin L Purves"
date: Sys.Date()
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: false
    number_sections: false
    highlight: monochrome
    theme: cerulean
code_folding: show

@@

```{r source file path}
#source data directory: data_path
source("../PANCHANGE_raw_path.R")
```

@@

#SB Hashing out this chunk of code as it is not included in our final analysis and is currently breaking the code.
```{r gad model0a absolute whole sample}
# Regression coefficients
#gad_baseline_model0a_estimates <- model0a.estimates(outcome = "gad.sum_score_base",
 #                                                data_set = "dat")
#kable(gad_baseline_model0a_estimates)
#gad_baseline_model0a_estimates

# Regression diagnostic statistics
#gad_baseline_model0a_reg_stats <- model0a.reg.stats(outcome = "gad.sum_score_base",
  #                                               data_set = "dat")
#kable(gad_baseline_model0a_reg_stats)
#gad_baseline_model0a_reg_stats
```

>>>>

---
title: "PANCHANGE_analysis"
author: "Katherine N Thompson, Christopher Hüebel, Molly R Davies, Kirstin L Purves"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: false
    number_sections: false
    highlight: monochrome
    theme: cerulean
code_folding: show

@@

```{r source file path}
#source data directory: data_path
source("../PANCHANGE_raw_path.R")

print(data_path)

@@

#SB Hashing out this chunk of code as it is not included in our final analysis and is currently breaking the code.
```{r gad model0a absolute whole sample}
# Regression coefficients
gad_baseline_model0a_estimates <- model0a.estimates(outcome = "gad.sum_score_base",
                                                 data_set = "dat")
#kable(gad_baseline_model0a_estimates)
gad_baseline_model0a_estimates

# Regression diagnostic statistics
gad_baseline_model0a_reg_stats <- model0a.reg.stats(outcome = "gad.sum_score_base",
                                                 data_set = "dat")
#kable(gad_baseline_model0a_reg_stats)
gad_baseline_model0a_reg_stats
```
